### 2016-11-23 local-capability-machine.tex
Added an empty proof
Updated Malloc specification so the footprint is a memory rather than a memory segment

\begin{specification}[Malloc v.2]
  $c_\malloc$ satisfies the specification for malloc iff
  \begin{align*}
    &\forall \Phi \in \ExecConfs \ldotp \forall \hsfoot, \hsframe \in \HeapSegments \ldotp \\
    &\quad \forall n, \size \in \nats \ldotp \forall b,e,a,m_b,m_e \in \Addrs\ldotp\forall p \in \Perms \ldotp \forall W \in \Worlds \ldotp\\
    &\qquad \exists i, \iota_{\malloc,0} \ldotp \\
    &\qquad \quad \forall W \future [i \mapsto \iota_{\malloc,0}] \land \\
%    &\qquad \quad \dom(\hsfoot) = [m_b,m_e] \land \\ % This
    &\qquad \quad \memheap = \hsfoot \uplus \hsframe \land\\
    &\qquad \quad \heapSat[\hsfoot]{n}{W} \land \\
    &\qquad \quad \memreg(r_1) = \size \land \\
    &\qquad \quad \size \geq 0 \land \\
    &\qquad \quad \memreg(r_0) = (p,b,e,a) \land \\
    &\qquad \quad \memreg(\pcreg) = c_\malloc \\ %and this needs to change with ABI.
    &\qquad \quad \Rightarrow \\
    &\qquad \qquad\exists \Phi' \in \ExecConfs \ldotp \exists \hsfoot' \in \HeapSegments\ldotp\\
    &\qquad \qquad \quad \exists j,k \in \nats \ldotp \exists b',e'\in \Addrs \ldotp \exists W' \in \Worlds \ldotp \\
    &\qquad \qquad \qquad \Phi \step[j]\Phi' \land \\
    &\qquad \qquad \qquad \memheap[\Phi']=\hsfoot'\uplus \hs_{\var{alloc}} \uplus \hsframe \land\\
    &\qquad \qquad \qquad W' = [i \mapsto \iota_{\malloc}']\land W' \futurewk W \land \\
    &\qquad \qquad \qquad \heapSat[\hsfoot']{n-j}{W'} \land \\
    &\qquad \qquad \qquad \dom(\hs_{\var{alloc}}) = [b',e'] \land \forall a \in [b',e']\ldotp \hs_{\var{alloc}}(a) = 0  \land \\
    &\qquad \qquad \qquad \memreg[\Phi'](\pcreg) = (\updatePcPerm{p},b,e,a) \land \\
    &\qquad \qquad \qquad \size = e'-b' \\
    &\qquad \qquad \qquad \memreg[\Phi'](r_1) = (\rwx,b',e',b') \land \\
    &\qquad \qquad \qquad \forall r \in \RegName \setminus \{\pcreg,r_1\} \ldotp \memreg[\Phi'](r) = 0
  \end{align*}

  Additionally, we require that for every $W' \future [i\mapsto \iota_{\malloc,0}]$, $\heapSat[\hs]{n}{W'}$ implies that $\dom(\hs)$ contains $[n',+\infty)$ for some $n'$.
\end{specification}
\lau{Only configurations with a memory (not memory segments) are executable. Therefore either $\hsfoot$ or $\hsframe$ need to be a memory and not a memory segment (it should probably be the footprint?).}

@@

\begin{lemma}[Correctness lemma for \texttt{f1}] \forcenewline
  For all $n \in \nats$
  let
  \begin{align*}
    c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+2) \\
    c_{f1} & \defeq ((\rwx,\glob),\mathtt{f1}-2,\mathtt{1f},\mathtt{f1}) \\
    c_\malloc & \defeq ((\entry,\glob),\start_\malloc,\addrend_\malloc,\start_\malloc+2) \\
    m & \defeq \hs_{f1} \uplus 
               \hs_\flag \uplus                
               \ms_{\var{link}} \uplus 
               \hs_\adv \uplus 
               m_{\malloc} \uplus 
               \hs_{\var{frame}} 
  \end{align*}
where 
\begin{align*}
  &\dom(\hs_{f1}) = [\mathtt{f1}-2,\mathtt{1f}] \\
  &\dom(\hs_\flag) = [\flag,\flag] \\
  &\dom(\ms_\link) = [\link,\link+1]\\
  &\dom(\hs_{\adv}) = [\start_\adv,\addrend_\adv] \\
  &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc}]} \text{ for all } n
\end{align*}
and
\begin{itemize}
\item The first address of $\hs_{f1}$ contains a global read-only capability for $\hs_\link$, the second address of $\hs_{f1}$ contains a global read-write capability to $\hs_\flag$, the rest of $\hs_{f1}$ contains the code of $f1$.
\item $\ms_\flag = [flag \mapsto 0]$
\item $\ms_{\var{link}} = [\var{link} \mapsto c_\malloc, \var{link} + 1 \mapsto c_\adv]$
\item $\hs_\adv$ contains a global read-only capability for $\hs_\link$ on its first address. The remaining cells of the memory segment only contain instructions.
\end{itemize}
if 
  \[
    (\reg_0\update{\pcreg}{c_{f1}},m) \step[n] (\halted,m'),
  \]
then
\[
  m'(\flag) = 0
\]  
\end{lemma}

>>>>

\begin{specification}[Malloc v.2]
  $c_\malloc$ satisfies the specification for malloc iff
  \begin{align*}
    &\forall \Phi \in \ExecConfs \ldotp \forall m_{\var{footprint}} \in \Heaps\ldotp \hsframe \in \HeapSegments \ldotp \\
    &\quad \forall n, \size \in \nats \ldotp \forall b,e,a \in \Addrs\ldotp\forall p \in \Perms \ldotp \forall W \in \Worlds \ldotp\\
    &\qquad \exists i, \iota_{\malloc,0} \ldotp \\
    &\qquad \quad \forall W \future [i \mapsto \iota_{\malloc,0}] \land \\
    &\qquad \quad \memheap = m_{\var{footprint}} \uplus \hsframe \land\\
    &\qquad \quad \heapSat[m_{\var{footprint}}]{n}{W} \land \\
    &\qquad \quad \memreg(r_1) = \size \land \\
    &\qquad \quad \size \geq 0 \land \\
    &\qquad \quad \memreg(r_0) = (p,b,e,a) \land \\
    &\qquad \quad \memreg(\pcreg) = c_\malloc \\ %and this needs to change with ABI.
    &\qquad \quad \Rightarrow \\
    &\qquad \qquad\exists \Phi' \in \ExecConfs \ldotp \exists m_{\var{footprint}}' \in \HeapSegments\ldotp\\
    &\qquad \qquad \quad \exists j,k \in \nats \ldotp \exists b',e'\in \Addrs \ldotp \exists W' \in \Worlds \ldotp \\
    &\qquad \qquad \qquad \Phi \step[j]\Phi' \land \\
    &\qquad \qquad \qquad \memheap[\Phi']=m_{\var{footprint}}' \uplus \hs_{\var{alloc}} \uplus \hsframe \land\\
    &\qquad \qquad \qquad W' = [i \mapsto \iota_{\malloc}']\land W' \futurewk W \land \\
    &\qquad \qquad \qquad \heapSat[m_{\var{footprint}}']{n-j}{W'} \land \\
    &\qquad \qquad \qquad \dom(\hs_{\var{alloc}}) = [b',e'] \land \forall a \in [b',e']\ldotp \hs_{\var{alloc}}(a) = 0  \land \\
    &\qquad \qquad \qquad \memreg[\Phi'](\pcreg) = (\updatePcPerm{p},b,e,a) \land \\
    &\qquad \qquad \qquad \size = e'-b' \\
    &\qquad \qquad \qquad \memreg[\Phi'](r_1) = (\rwx,b',e',b') \land \\
    &\qquad \qquad \qquad \forall r \in \RegName \setminus \{\pcreg,r_1\} \ldotp \memreg[\Phi'](r) = 0
  \end{align*}

  Additionally, we require that for every $W' \future [i\mapsto \iota_{\malloc,0}]$, $\heapSat[\hs]{n}{W'}$ implies that $\dom(\hs)$ contains $[n',+\infty)$ for some $n'$.
\end{specification}

@@

\begin{lemma}[Correctness lemma for \texttt{f1}] \forcenewline
\label{lem:correctness-f1}
  For all $n \in \nats$
  let
  \begin{align*}
    c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+2) \\
    c_{f1} & \defeq ((\rwx,\glob),\mathtt{f1}-2,\mathtt{1f},\mathtt{f1}) \\
    c_\malloc & \defeq ((\entry,\glob),\start_\malloc,\addrend_\malloc,\start_\malloc+2) \\
    m & \defeq \hs_{f1} \uplus 
               \hs_\flag \uplus                
               \ms_{\var{link}} \uplus 
               \hs_\adv \uplus 
               m_{\malloc} \uplus 
               \hs_{\var{frame}} 
  \end{align*}
where 
\begin{align*}
  &\dom(\hs_{f1}) = [\mathtt{f1}-2,\mathtt{1f}] \\
  &\dom(\hs_\flag) = [\flag,\flag] \\
  &\dom(\ms_\link) = [\link,\link+1]\\
  &\dom(\hs_{\adv}) = [\start_\adv,\addrend_\adv] \\
  &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc}]} \text{ for all } n
\end{align*}
and
\begin{itemize}
\item The first address of $\hs_{f1}$ contains a global read-only capability for $\hs_\link$, the second address of $\hs_{f1}$ contains a global read-write capability to $\hs_\flag$, the rest of $\hs_{f1}$ contains the code of $f1$.
\item $\ms_\flag = [flag \mapsto 0]$
\item $\ms_{\var{link}} = [\var{link} \mapsto c_\malloc, \var{link} + 1 \mapsto c_\adv]$
\item $\hs_\adv$ contains a global read-only capability for $\hs_\link$ on its first address. The remaining cells of the memory segment only contain instructions.
\end{itemize}
if 
  \[
    (\reg_0\update{\pcreg}{c_{f1}},m) \step[n] (\halted,m'),
  \]
then
\[
  m'(\flag) = 0
\]  
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:correctness-f1}]

\end{proof}
